---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ssdsuite

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/ssdsuite/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/ssdsuite/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of ssdsuite is to facilitate installation and loading of species sensitivity distribution data and software.

## Installation

You can install `ssdsuite` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("poissonconsulting/ssdsuite")
```

You can install `ssdsuite` from [R-universe](https://poissonconsulting.r-universe.dev/builds) with:

```r
install.packages("ssdsuite", repos = "https://poissonconsulting.r-universe.dev", type = "source")
```

### Usage

To load `ssdsuite`

```{r}
library(ssdsuite)
```

### Packages

The packages installed and loaded by `ssdsuite` suite are:

- [envirotox](https://github.com/poissonconsulting/envirotox)
- [shinyssdtools](https://github.com/bcgov/shinyssdtools)
- [ssddata](https://github.com/open-AIMS/ssddata)
- [ssdsims](https://github.com/poissonconsulting/ssdsims)
- [ssdtests](https://github.com/poissonconsulting/ssdtests)
- [ssdtools](https://github.com/bcgov/ssdtools)
- [ssdvignettes](https://github.com/poissonconsulting/ssdvignettes)

## Contribution

Please report any [issues](https://github.com/poissonconsulting/ssdsuite/issues).

[Pull requests](https://github.com/poissonconsulting/ssdsuite/pulls) are always welcome.

## Code of Conduct

Please note that the `ssdsuite` project is released with a [Contributor Code of
Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

```{r, results = "asis", echo = FALSE}
cat(ssdsuite::licensing_md())
```
